External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-27 CVPR2017_Review_Unified.tex
add

Here we take a detailed analysis on the guiance of the external patch group (PG) prior for the internal noisy PGs of given real noisy images. The guidance comes from at least three aspects: 1) the external prior guides the internal PGs to be clustered into suitable subspaces through MAP in Equ. (\ref{equ5}). The guided subspace clustering is more efficient than directly clustering the internal noisy PGs via k-means or Gaussian Mixture Model (GMM). The reason is, by guidance we only need calculate the probabilities via Equ. (\ref{equ5}) for all noisy PGs while by internal clustering via GMM we need perform EM algorithm \cite{em}. 2) under the guidance of external orthogonal dictionary, the learned internal dictioary are also orthogonal and more adaptive to the given noisy images. This makes the learning process very efficient. Besides, the learned orthogonal dictionary can also makes the denoising process very efficient. 3) the singular values obtained by SVD in Equ. (\ref{equ3}) reflect the prior importance of the atoms in learned dictionary and hence can be used as adaptive parameters in the sparse coding framework for real image denoising.

>>>>

Here we take a detailed analysis on the guiance of the external patch group (PG) prior for the internal noisy PGs of given real noisy images. The guidance comes from at least three aspects: 1) the external prior guides the internal PGs to be clustered into suitable subspaces through MAP in Equ. (\ref{equ5}). The guided subspace clustering is more efficient than directly clustering the internal noisy PGs via k-means or Gaussian Mixture Model (GMM). The reason is, by guidance we only need calculate the probabilities via Equ. (\ref{equ5}) for all noisy PGs while by internal clustering via GMM we need perform EM algorithm \cite{em}. 2) the external dictionary guides the internal dictionary learning, and the obtained dictionary consisted of the two parts is orthogonal and more adaptive to the given noisy image. The learning process has closed-form solutions and hence is very efficient. Besides, the learned orthogonal dictionary also makes the denoising process very efficient under sparse coding framework. 3) the singular values obtained by SVD in Equ. (\ref{equ3}) reflect the prior weights of the atoms in learned dictionary and can be used as adaptive parameters for real image denoising.
